Paper Analysis

### 2024-07-15 Paper_WriteUp/Paper_Plots.qmd
add some more details looking at the proportion of games started within 3 minutes for bullet and 7 minutes for blitz

@@

>>>>

 bullet_data |>  group_by(Username) |> 
  select(Username, UTCDate, UTCTime) |> 
  mutate(date_time = ymd_hms(paste(UTCDate, UTCTime))) |> 
  group_by(Username) |> 
  arrange(date_time) |> 
  mutate(gap = date_time - lag(date_time),
         gap_seconds = as.numeric(gap)) |> 
  mutate(less_3 = ifelse(gap_seconds <= 180, TRUE, FALSE)) |> 
  ungroup() |>   ## to get the overall proportion
  summarise(sum(less_3, na.rm = TRUE)/ n()) |> 
  print(n = 25)

@@

## look at the proportion of games started within 3 minutes 
## of the previous game
bullet_data_gm |> 
  # group_by(Username) |> 
  select(Username, UTCDate, UTCTime) |> 
  mutate(date_time = ymd_hms(paste(UTCDate, UTCTime))) |> 
  group_by(Username) |> 
  arrange(date_time) |> 
  mutate(gap = date_time - lag(date_time),
         gap_seconds = as.numeric(gap)) |> 
  mutate(less_3 = ifelse(gap_seconds <= 180, TRUE, FALSE)) |> 
  ungroup() |>   ## to get the overall proportion
  summarise(sum(less_3, na.rm = TRUE)/ n()) |> 
  print(n = 25)

## look at the streaks, number of games played in a session
outcomes <- bullet_data_gm |> 
  # group_by(Username) |> 
  select(Username, UTCDate, UTCTime) |> 
  mutate(date_time = ymd_hms(paste(UTCDate, UTCTime))) |> 
  group_by(Username) |> 
  arrange(date_time) |> 
  mutate(gap = date_time - lag(date_time),
         gap_seconds = as.numeric(gap)) |> 
  mutate(less_3 = if_else(gap_seconds <= 180, TRUE, FALSE, FALSE))

get_true_sequences <- function(x) {
  rle_x <- rle(x)
  true_lengths <- rle_x$lengths[rle_x$values == TRUE]
  return(true_lengths)
}

# Apply function to each group
result <- outcomes %>%
  # group_by(group) %>%
  summarise(session_length = list(get_true_sequences(less_3)))

result |> 
  unnest_longer(session_length) |> 
  ggplot(aes(session_length)) +
  geom_histogram()

result |> 
  unnest_longer(session_length) |> 
  mutate(multiple = if_else(session_length > 1, TRUE, FALSE)) |> 
  # group_by(Username) |> 
  summarise(sum(multiple)/n())

outcomes_blitz <- blitz_data_gm |> 
  # group_by(Username) |> 
  select(Username, UTCDate, UTCTime) |> 
  mutate(date_time = ymd_hms(paste(UTCDate, UTCTime))) |> 
  group_by(Username) |> 
  arrange(date_time) |> 
  mutate(gap = date_time - lag(date_time),
         gap_seconds = as.numeric(gap)) |> 
  mutate(less_7_min = if_else(gap_seconds <= 420, TRUE, FALSE, FALSE))

# Apply function to each group
result_blitz <- outcomes_blitz %>%
  # group_by(group) %>%
  summarise(session_length = list(get_true_sequences(less_7_min)))

result_blitz |> 
  unnest_longer(session_length) |> 
  ggplot(aes(session_length)) +
  geom_histogram()

result_blitz |> 
  unnest_longer(session_length) |> 
  mutate(multiple = if_else(session_length > 1, TRUE, FALSE)) |> 
  # group_by(Username) |> 
  summarise(sum(multiple)/n())
